### 2018-12-31 Sections/QTCP_protocol_stack.tex
indexing

The structure of the protocol stack for QTCP is shown in Fig.~\ref{fig:stack}. In summary, the layers in the protocol stack are, beginning from the lowest level:
\begin{itemize}
\item \textsc{Data (Message)}\index{Data (message) layer}: Raw data (`payload') Alice wishes to transmit to Bob. Comprises both \textsc{Quantum Data}\index{Quantum data layer} and \textsc{Classical Data}\index{Classical data layer}.
\item \textsc{Packet}\index{Packet!Layer}: Decomposition of \textsc{Data} into blocks (\textsc{Packet Data}\index{Packet!Data layer}), and associated classical \textsc{Packet Headers}\index{Packet!Header layer} containing metadata (e.g routing information).
\item \textsc{Strategy}\index{Strategy!Layer}: Construct \textsc{Packet} routing strategies based on a cost optimisation algorithm.
\item \textsc{Transport}\index{Transport layer}: Physical routing of \textsc{Packets} to arrive at their destination, based upon metadata contained in \textsc{Packet Header}. Perform collision detection during transit.
\item \textsc{Reconstruction}\index{Reconstruction layer}: Reconstruct \textsc{Data} from received \textsc{Packets}.
\item \textsc{Quality of Service (QoS)}\index{Quality of service (QoS) layer}: Apply QEC and determine whether \textsc{QoS} requirements have been satisfied.
\item \textsc{Services \& Applications}\index{Services \& applications layer}: High-level interface to \textsc{Data} presented to Bob's services and applications. The interface abstracts away lower levels of the protocol stack, presenting Bob with only \textsc{Data} and its associated metadata.
\end{itemize}

@@

\subsubsection{Quality of service} \label{sec:QOS} \index{Quality of service (QoS) layer}

>>>>

The structure of the protocol stack for QTCP is shown in Fig.~\ref{fig:stack}. In summary, the layers in the protocol stack are, beginning from the lowest level:
\begin{itemize}
\item \textsc{Data (Message)}\index{Data (message) layer}: Raw data (`payload') Alice wishes to transmit to Bob. Comprises both \textsc{Quantum Data}\index{Quantum data layer} and \textsc{Classical Data}\index{Classical data layer}.
\item \textsc{Packet}\index{Packet!Layer}: Decomposition of \textsc{Data} into blocks (\textsc{Packet Data}\index{Packet!Data layer}), and associated classical \textsc{Packet Headers}\index{Packet!Header layer} containing metadata (e.g routing information).
\item \textsc{Strategy}\index{Strategy!Layer}: Construct \textsc{Packet} routing strategies based on a cost optimisation algorithm.
\item \textsc{Transport}\index{Transport layer}: Physical routing of \textsc{Packets} to arrive at their destination, based upon metadata contained in \textsc{Packet Header}. Perform collision detection during transit.
\item \textsc{Reconstruction}\index{Reconstruction layer}: Reconstruct \textsc{Data} from received \textsc{Packets}.
\item \textsc{Quality of Service (QoS)}\index{Quality of service (QoS)!Layer}: Apply QEC and determine whether \textsc{QoS} requirements have been satisfied.
\item \textsc{Services \& Applications}\index{Services \& applications layer}: High-level interface to \textsc{Data} presented to Bob's services and applications. The interface abstracts away lower levels of the protocol stack, presenting Bob with only \textsc{Data} and its associated metadata.
\end{itemize}

@@

\subsubsection{Quality of service} \label{sec:QOS} \index{Quality of service (QoS)!Layer}

### 2018-12-31 Sections/cryptowars.tex
Added authors to sections
indexing

Hash functions have broad applicability throughout computer science, but here we are most interested in \textit{cryptographic hash functions} for use in cryptography, which impose strong conditions on the difficulty of inversion and their quasi-random characteristics. Most notably, the desired characteristics of a cryptographic hash function include:
\begin{itemize}
	\item The distribution of hashes ought not exhibit any biases, following a uniform distribution with quasi-random\index{Quasi-random} behaviour.
	\item Changing a single bit in the input string ought to flip approximately half the bits of the hash on average.	
	\item It's computationally efficient to calculate a hash from an input.
	\item It's computationally complex to find an input that hashes to a given value (that is, they are one-way or trapdoor functions).\index{Trapdoor functions}
	\item The hashes of two very similar inputs ought to yield hashes that a very different.
	\item Two different inputs are extremely unlikely to hash to the same value.
\end{itemize}

>>>>

Hash functions have broad applicability throughout computer science, but here we are most interested in \textit{cryptographic hash functions} for use in cryptography, which impose strong conditions on the difficulty of inversion and their quasi-random characteristics. Most notably, the desired characteristics of a cryptographic hash function include:
\begin{itemize}
	\item The distribution of hashes ought not exhibit any biases, following a uniform distribution with quasi-random\index{Quasi-randomness} behaviour.
	\item Changing a single bit in the input string ought to flip approximately half the bits of the hash on average.	
	\item It's computationally efficient to calculate a hash from an input.
	\item It's computationally complex to find an input that hashes to a given value (that is, they are one-way or trapdoor functions).\index{One-way functions}
	\item The hashes of two very similar inputs ought to yield hashes that a very different.
	\item Two different inputs are extremely unlikely to hash to the same value.
\end{itemize}

### 2018-12-31 Sections/essay_the_economics_of_the_quantum_internet.tex
indexing

Already today, even before the advent of useful post-classical quantum computers, we are seeing the emergence of the outsourced model for computation\index{Outsourced!Quantum computation}. IBM recently made an elementary 16-qubit quantum computer freely available for use via the cloud. Interested users can log in online, upload a circuit description for a quantum protocol, and have it executed remotely, with the results relayed back in real-time. Although still very primitive, this simple development already makes experimentation with elementary quantum protocols accessible to the poor layman, undergrad, or PhD student in a developing country, people who just a few years ago would never have dreamt of being able to run their own quantum information processing experiments! This effectively opens up research opportunities to people who otherwise would have been priced out of the market entirely, unable to compete with established, well-resourced labs. Evidently, the market already recognises the importance of outsourced models for quantum computation. We encourage the impatiently curious reader to log onto the `IBM Quantum Experience'\index{IBM Quantum Experience} (\href{http://www.research.ibm.com/quantum/}{http://www.research.ibm.com/quantum/}) and take a shot at designing a 16-qubit quantum protocol, without even needing to be in the same country as the quantum computer.

>>>>

Already today, even before the advent of useful post-classical quantum computers, we are seeing the emergence of the outsourced model for computation\index{Outsourced!Quantum computation}. IBM recently made an elementary 16-qubit quantum computer freely available for use via the cloud. Interested users can log in online, upload a circuit description for a quantum protocol, and have it executed remotely, with the results relayed back in real-time. Although still very primitive, this simple development already makes experimentation with elementary quantum protocols accessible to the poor layman, undergrad, or PhD student in a developing country, people who just a few years ago would never have dreamt of being able to run their own quantum information processing experiments! This effectively opens up research opportunities to people who otherwise would have been priced out of the market entirely, unable to compete with established, well-resourced labs. Evidently, the market already recognises the importance of outsourced models for quantum computation. We encourage the impatiently curious reader to log onto the `IBM Quantum Experience'\index{IBM!Quantum Experience} (\href{http://www.research.ibm.com/quantum/}{http://www.research.ibm.com/quantum/}) and take a shot at designing a 16-qubit quantum protocol, without even needing to be in the same country as the quantum computer.

### 2018-12-31 Sections/essays_quantum_ecosystem.tex
indexing

\item Oracles:\index{Oracles} as an essential quantum software building block, oracles will become a fundamental unit for outsourcing. These oracles will store hard-corded or algorithmically-generated databases, or mathematical functions. For example, for use in genetic medicine (Sec.~\ref{sec:genetic_medicine}), such databases could algorithmically generate tables of candidate drug compounds, or they could implement mathematical functions whose input space is to be searched over when quantum-enhancing the solving of \textbf{NP}-complete\index{NP and NP-complete} problems.

@@

\item Classical pre-, post- or intermediate-processing:\index{Classical processing} quantum computation, and other quantum protocols, typically require some degree of classical pre- or post-processing. These classical operations can be highly non-trivial. For example, a novel topological quantum error correcting code\index{Quantum error correction} (Sec.~\ref{sec:surface_codes}) might require complex encoding, decoding and feedforward operations. Determining and implementing these operations may require complicated optimisation protocols. These might be outsourced to a specialised provider.

@@

\item Quantum error correction:\index{Quantum error correction} any given quantum error correcting code follows a well-defined recipe for encoding, correction, and decoding. Thus, it might become an example of a subroutine specialised in by a dedicated quantum error correction vendor, and licensed out as a building block for embedding into larger, fault-tolerant\index{Fault-tolerance} protocols.

>>>>

\item Oracles:\index{Oracles} as an essential quantum software building block, oracles will become a fundamental unit for outsourcing. These oracles will store hard-corded or algorithmically-generated databases, or mathematical functions. For example, for use in genetic medicine (Sec.~\ref{sec:genetic_medicine}), such databases could algorithmically generate tables of candidate drug compounds, or they could implement mathematical functions whose input space is to be searched over when quantum-enhancing the solving of \textbf{NP}-complete\index{NP \& NP-complete} problems.

@@

\item Classical pre-, post- or intermediate-processing:\index{Classical processing} quantum computation, and other quantum protocols, typically require some degree of classical pre- or post-processing. These classical operations can be highly non-trivial. For example, a novel topological quantum error correcting code\index{Quantum error correction (QEC)} (Sec.~\ref{sec:surface_codes}) might require complex encoding, decoding and feedforward operations. Determining and implementing these operations may require complicated optimisation protocols. These might be outsourced to a specialised provider.

@@

\item Quantum error correction:\index{Quantum error correction (QEC)} any given quantum error correcting code follows a well-defined recipe for encoding, correction, and decoding. Thus, it might become an example of a subroutine specialised in by a dedicated quantum error correction vendor, and licensed out as a building block for embedding into larger, fault-tolerant\index{Fault-tolerance} protocols.

### 2018-12-31 Sections/how_to_learn_more.tex
indexing

\begin{itemize}
	\item SimulaQron\index{SimulaQron} (\href{http://www.simulaqron.org}{http://www.simulaqron.org}): Developed by QuTech Delft \cite{bib:AxelDahlbergQron}, a simulator for designing software for the quantum internet. The package includes its own quantum internet programming language for deploying networked quantum algorithms. The institute runs competitions for designing the best quantum internet app.
	\item Google Cirq\index{Cirq} (\href{https://github.com/quantumlib/Cirq}{https://github.com/quantumlib/Cirq}): Google's Python-based SDK for designing quantum software, specifically targeted at development for Google's own in-house quantum computing hardware platform.
	\item Microsoft Quantum Development Kit and the Q\# language\index{Q\#}\index{Microsoft Quantum Development Kit} (\href{https://www.microsoft.com/en-au/quantum/development-kit}{https://www.microsoft.com/en-au/quantum/development-kit}): a full SDK for writing code executable on quantum computers. The Q\# language is used to describe quantum operations, which classical code written in C\#\index{C\#} can interface with and control. The platform is extremely versatile and allows highly complex quantum operations to be coded in a high-level, platform-independent manner. The platform includes a simulator for executing code for which the hardware doesn't yet exist.
	\item IBM Quantum Experience\index{IBM Quantum Experience} (\href{http://www.research.ibm.com/quantum/}{http://www.research.ibm.com/quantum/}): IBM's cloud-based platform for remotely executing simple quantum protocols, as written and uploaded to the cloud by the user. The platform includes QISKit, a Python-based SDK for executing quantum algorithms. It is based on the Open Quantum Assembly Language (OpenQASM) language\index{OpenQASM}.
	\item Rigetti Quantum Cloud Services (QCS)\index{Rigetti Quantum Cloud Services} (\href{https://www.rigetti.com/qcs}{https://www.rigetti.com/qcs}): Rigetti's cloud platform for accessing and deploying algorithms to their hardware over the cloud. Development is powered by the Forest SDK\index{Forest SDK}, their own in-house development platform.
	\item Keep looking, as the list is rapidly growing with new participants entering the market\ldots
\end{itemize}

>>>>

\begin{itemize}
	\item SimulaQron\index{SimulaQron} (\href{http://www.simulaqron.org}{http://www.simulaqron.org}): Developed by QuTech Delft \cite{bib:AxelDahlbergQron}, a simulator for designing software for the quantum internet. The package includes its own quantum internet programming language for deploying networked quantum algorithms. The institute runs competitions for designing the best quantum internet app.
	\item Google Cirq\index{Cirq} (\href{https://github.com/quantumlib/Cirq}{https://github.com/quantumlib/Cirq}): Google's Python-based SDK for designing quantum software, specifically targeted at development for Google's own in-house quantum computing hardware platform.
	\item Microsoft Quantum Development Kit and the Q\# language\index{Q\#}\index{Microsoft Quantum Development Kit} (\href{https://www.microsoft.com/en-au/quantum/development-kit}{https://www.microsoft.com/en-au/quantum/development-kit}): a full SDK for writing code executable on quantum computers. The Q\# language is used to describe quantum operations, which classical code written in C\#\index{C\#} can interface with and control. The platform is extremely versatile and allows highly complex quantum operations to be coded in a high-level, platform-independent manner. The platform includes a simulator for executing code for which the hardware doesn't yet exist.
	\item IBM Quantum Experience\index{IBM!Quantum Experience} (\href{http://www.research.ibm.com/quantum/}{http://www.research.ibm.com/quantum/}): IBM's cloud-based platform for remotely executing simple quantum protocols, as written and uploaded to the cloud by the user. The platform includes QISKit, a Python-based SDK for executing quantum algorithms. It is based on the Open Quantum Assembly Language (OpenQASM) language\index{OpenQASM}.
	\item Rigetti Quantum Cloud Services (QCS)\index{Rigetti Quantum Cloud Services} (\href{https://www.rigetti.com/qcs}{https://www.rigetti.com/qcs}): Rigetti's cloud platform for accessing and deploying algorithms to their hardware over the cloud. Development is powered by the Forest SDK\index{Forest SDK}, their own in-house development platform.
	\item Keep looking, as the list is rapidly growing with new participants entering the market regularly\ldots
\end{itemize}

### 2018-12-31 Sections/index.tex
Intro to QO
Formatting update
indexing

@@

\index{Single-photons \seeonly{Photons}|gobbleone}

@@

\index{Functional group libraries \seeonly{Drug compound libraries}|gobbleone}

@@

\index{Entanglement distillation \seeonly{Entanglement purification}|gobbleone}

@@

\index{Cluster state!Fusion strategies \seeonly{Fusion strategies}|gobbleone}

@@

\index{Period-finding  @\also{Shor's algorithm}|gobbleone}
\index{Robustness @\also{Network robustness}|gobbleone}
\index{Message digests @\also{Checksum}|gobbleone}
\index{Collisions @\also{Hash collisions}|gobbleone}
\index{Checksum @\also{Hash functions}|gobbleone}
\index{Black box @\also{Oracle}|gobbleone}
\index{Thermal noise @\also{Errors}|gobbleone}
\index{Synthetic aperture @\also{Quantum-enhanced telescopy}|gobbleone}
\index{Ledger @\also{Distributed ledger}|gobbleone}
\index{Integer factorisation @\also{Shor's algorithm}|gobbleone}
\index{Human genome project @\also{Genome}|gobbleone}
\index{Enigma machines @\also{Quantum Enigma machines}|gobbleone}
\index{Efficiency @\also{Loss channel, detector efficiency, computational efficiency}|gobbleone}
\index{Cryptanalysis @\also{Differential cryptanalysis, linear cryptanalysis, frequency analysis}|gobbleone}
\index{Quantum Moore's Law @\also{Moore's Law}|gobbleone}
\index{Toric code @\also{Topological codes, surface codes}|gobbleone}
\index{Surface codes @\also{Topological codes}|gobbleone}
\index{Distributed unitary error averaging @\also{Unitary error averaging}|gobbleone}
\index{Nano-satellites @\also{Micro-satellites}|gobbleone}
\index{Micro-satellites @\also{Nano-satellites}|gobbleone}
\index{Two-channel two-port switches @\also{Optical routers}|gobbleone}
\index{Multiplexers @\also{Optical routers}|gobbleone}
\index{Demultiplexers @\also{Optical routers}|gobbleone}
\index{Linear multiplexers \& demultiplexers @\also{Optical routers}|gobbleone}
\index{Pyramid multiplexers \& demultiplexers @\also{Optical routers}|gobbleone}
\index{Single-channel multi-port switches @\also{Optical routers}|gobbleone}
\index{Multi-channel multi-port switches @\also{Optical routers}|gobbleone}
\index{Quantum error correction (QEC) @\also{3-qubit code, 5-qubit code, 7-qubit code, 9-qubit code, topological codes, unitary error averaging}|gobbleone}
\index{Homomorphic encryption @\also{Encrypted quantum computation}|gobbleone}
\index{Blind quantum computation @\also{Encrypted quantum computation}|gobbleone}
\index{Phase!Key encoding @\also{Encrypted quantum computation}|gobbleone}
\index{Polarisation-key encoding @\also{Encrypted quantum computation}|gobbleone}
\index{Displacement-key encoding @\also{Encrypted quantum computation}|gobbleone}
\index{Non-optical encodings @\also{Matter qubits}|gobbleone}
\index{Time-dependent quantum computational leverage @\also{Quantum computational leverage}|gobbleone}
\index{Distance to horizon @\also{Line-of-sight}|gobbleone}
\index{Line-of-sight @\also{Distance to horizon}|gobbleone}
\index{Micro-cluster states @\also{Star micro-cluster states, plus micro-cluster states, linear micro-cluster states, snowflake micro-cluster states}|gobbleone}
\index{Star micro-cluster states @\also{Micro-cluster states}|gobbleone}
\index{Plus micro-cluster states @\also{Micro-cluster states}|gobbleone}
\index{Linear micro-cluster states @\also{Micro-cluster states}|gobbleone}
\index{Snowflake micro-cluster states @\also{Micro-cluster states}|gobbleone}
\index{Single-qubit quantum computational leverage @\also{Quantum computational leverage}|gobbleone}
\index{Time-dependent quantum computational leverage @\also{Quantum computational leverage}|gobbleone}
\index{Quality of service (QoS) @\also{Quantum error correction, entanglement purification}|gobbleone}
\index{Anonymous surveys @\also{Quantum voting}|gobbleone}
\index{Binary voting @\also{Quantum voting}|gobbleone}

>>>>

\index{Self-interference \seeonly{Mach-Zehnder (MZ) interference}|gobbleone}
\index{Heisenberg!Uncertainty principle \seeonly{Uncertainty principle}|gobbleone}
\index{Fock state \seeonly{Photon-number state}|gobbleone}

@@

@@

\index{Functional groups!Libraries \seeonly{Drug compound libraries}|gobbleone}

@@

@@

\index{Cluster states!Fusion strategies \seeonly{Fusion strategies}|gobbleone}

@@

\index{Single-photons @\also{Photons}|gobbleone}
\index{Period-finding  @\also{Shor's algorithm}|gobbleone}
\index{Robustness @\also{Network robustness}|gobbleone}
\index{Message digests @\also{Checksum}|gobbleone}
\index{Collisions @\also{Hash collisions}|gobbleone}
\index{Checksum @\also{Hash functions}|gobbleone}
\index{Black box @\also{Oracle}|gobbleone}
\index{Thermal noise @\also{Errors}|gobbleone}
\index{Synthetic aperture @\also{Quantum-enhanced telescopy}|gobbleone}
\index{Ledger @\also{Distributed ledger}|gobbleone}
\index{Integer factorisation @\also{Shor's algorithm}|gobbleone}
\index{Human genome project @\also{Genome}|gobbleone}
\index{Enigma machines @\also{Quantum Enigma machines}|gobbleone}
\index{Efficiency @\also{Loss channel, detector efficiency, computational efficiency}|gobbleone}
\index{Cryptanalysis @\also{Differential cryptanalysis, linear cryptanalysis, frequency analysis}|gobbleone}
\index{Quantum Moore's Law @\also{Moore's Law}|gobbleone}
\index{Toric code @\also{Topological codes, surface codes}|gobbleone}
\index{Surface codes @\also{Topological codes}|gobbleone}
\index{Distributed unitary error averaging @\also{Unitary error averaging}|gobbleone}
\index{Nano-satellites @\also{Micro-satellites}|gobbleone}
\index{Micro-satellites @\also{Nano-satellites}|gobbleone}
\index{Two-channel two-port switches @\also{Optical routers}|gobbleone}
\index{Multiplexers @\also{Optical routers}|gobbleone}
\index{Demultiplexers @\also{Optical routers}|gobbleone}
\index{Linear multiplexers \& demultiplexers @\also{Optical routers}|gobbleone}
\index{Pyramid multiplexers \& demultiplexers @\also{Optical routers}|gobbleone}
\index{Single-channel multi-port switches @\also{Optical routers}|gobbleone}
\index{Multi-channel multi-port switches @\also{Optical routers}|gobbleone}
\index{Quantum error correction (QEC) @\also{3-qubit code, 5-qubit code, 7-qubit code, 9-qubit code, topological codes, unitary error averaging}|gobbleone}
\index{Homomorphic encryption @\also{Encrypted quantum computation}|gobbleone}
\index{Blind quantum computation @\also{Encrypted quantum computation}|gobbleone}
\index{Phase!Key encoding @\also{Encrypted quantum computation}|gobbleone}
\index{Polarisation-key encoding @\also{Encrypted quantum computation}|gobbleone}
\index{Displacement-key encoding @\also{Encrypted quantum computation}|gobbleone}
\index{Non-optical encodings @\also{Matter qubits}|gobbleone}
\index{Time-dependent quantum computational leverage @\also{Quantum computational leverage}|gobbleone}
\index{Distance to horizon @\also{Line-of-sight}|gobbleone}
\index{Line-of-sight @\also{Distance to horizon}|gobbleone}
\index{Micro-cluster states @\also{Star micro-cluster states, plus micro-cluster states, linear micro-cluster states, snowflake micro-cluster states}|gobbleone}
\index{Star micro-cluster states @\also{Micro-cluster states}|gobbleone}
\index{Plus micro-cluster states @\also{Micro-cluster states}|gobbleone}
\index{Linear micro-cluster states @\also{Micro-cluster states}|gobbleone}
\index{Snowflake micro-cluster states @\also{Micro-cluster states}|gobbleone}
\index{Single-qubit quantum computational leverage @\also{Quantum computational leverage}|gobbleone}
\index{Time-dependent quantum computational leverage @\also{Quantum computational leverage}|gobbleone}
\index{Quality of service (QoS) @\also{Quantum error correction, entanglement purification}|gobbleone}
\index{Anonymous surveys @\also{Quantum voting}|gobbleone}
\index{Binary voting @\also{Quantum voting}|gobbleone}
